\Title

### 2016-02-26 manuscript/manuscript.tex
Finish first draft of introduction
Fixes #3

@@

A similar approach was used by \citet{martins2010}
to estimate the parameters defining
the density-contrast variation with depth
of a sedimentary basin.
\citet{vandermeijde2013} also had
a similar methodology for dealing with the hyper-parameters,
though in a less formalized way.

>>>>

We present a non-linear gravity inversion to estimate the Moho depth in
a spherical Earth approximation.
Our method is based on the \citet{silva2014} Gauss-Newton formulation of the
method of \citet{bott1960}.
We use tesseroids to discretize the anomalous Moho and the adaptive
discretization algorithm of \citet{uieda2016} for the forward modeling.
The stability of the inversion is achieved through smoothness regularization.
In order to maintain the computational efficiency of Bott's method,
we exploit the sparse nature of all matrices involved in the computations.
We employ a variant of GCV known as hold-out cross-validation \citep{kim2009}
to estimate the regularization parameter.
Additionally, we estimate the density-contrast and reference level
simultaneously in a second cross-validation.
Similarly to \citet{silva2006} and \citet{martins2010}, this cross-validation
procedure uses knowledge of the Moho depth at certain points.
Finally, we apply the proposed method to estimate the Moho depth for South
America using gravity data from the GOCO5S model \citep{mayer-guerr2015} and
the seismological data of \citet{assumpcao2013a}.

@@

A similar approach was used by \citet{silva2006} and \citet{martins2010}
to estimate the parameters defining
the density-contrast variation with depth
of a sedimentary basin.
\citet{vandermeijde2013} also had
a similar methodology for dealing with the hyper-parameters,
though in a less formalized way.
